rotation_runs2019

### 2019-10-07 inst/documents/rotation_runs2019.Rmd
improving experiment outputs

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5.5, comment=NA, results='asis'}

@@

# now specify an experiment from the multi-experiment file
id_expt <- 'A2'
#id_expt <- 'A4'

@@

@@

    #code to rerun approx this scenario
    cat(paste0("run_rot(n_insecticides=",linputs$n_insecticides,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "cost=",signif(linputs$cost,2),", ",
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "rot_interval=",linputs$rot_interval,", ",
                "eff=",signif(linputs$eff,2),",\n",
                "dom_sel=",signif(linputs$dom_sel,2),", ",
                "dom_cos=",signif(linputs$dom_cos,2),", ",
                "rr=",signif(linputs$rr,2),", ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "coverage=",signif(linputs$coverage,2),",\n",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "min_rwr_interval=",linputs$min_rwr_interval,            
                ")\n\n") )

>>>>

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5.4, comment=NA, results='asis'}

@@

# now specify an experiment from the multi-experiment file
#id_expt <- 'A2'
#id_expt <- 'A4'
id_expt <- 'B2'

# to move the pdf of a preceeding run of this file to a saved location
# RUN the line above and below after knitting the file
# ASSUMING id_expt still set to previous run and still same day
# BEWARE that id_expt will not be set correctly in home env if file was knitted
#file.rename("rotation_runs2019.pdf",paste0(outFolder,format(Sys.time(), "%Y-%m-%d-"),id_expt,"-results-figs.pdf"))

@@

cat("\nNumbers on the right are the number of generations that this insecticide is in use and the corresponding resistance is below threshold.\n   ")

cat("\nOn each page a Sequence is at the top and an annual Rotation at the bottom.")

@@

    #code to rerun approx this scenario, can be copied from pdf and pasted into R
    #has to cope with converting vectors to strings
    #spaces between args stop the pdf from messing with words
    cat(paste0("run_rot(n_insecticides=",linputs$n_insecticides,", ",
                "rot_interval=",linputs$rot_interval,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "cost=c(",paste(signif(linputs$cost,2),collapse=','),"), ", 
                "eff=c(",paste(signif(linputs$eff,2),collapse=','),"), ",               
                "dom_sel=c(",paste(signif(linputs$dom_sel,2),collapse=','),"), ",
                "dom_cos=c(",paste(signif(linputs$dom_cos,2),collapse=','),"), ",
                "rr=c(",paste(signif(linputs$rr,2),collapse=','),"), ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "coverage=",signif(linputs$coverage,2),", ",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "min_rwr_interval=",linputs$min_rwr_interval,            
                ")\n\n") )
